Brownian Dynein Model

### 2015-09-29 latex/derivation.tex
Start of work on derivation.tex

\begin{align}
  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) - \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}+\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
\end{align}

>>>>

\begin{align}
  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) \mp \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
\end{align}

We simplify...

\begin{align}
  X_{nm} &= \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2L}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\Big) \mp \sqrt{L_{n}^2-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2L}\bigg)^2}\sqrt{L_{n}^2-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\bigg)^2} \Bigg) \\
  Y_{nm} &= \frac{L_{s}}{L_{n}}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\sqrt{L_{n}^2-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2L}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2L}\sqrt{L_{n}^2-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\bigg)^2} \Bigg) \\
\end{align}

We then expand $L_{n}$...

\begin{align}
  X_{nm} &= \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\Big)\Big(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\Big) \mp \\
  & \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\bigg)^2}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\bigg)^2} \Bigg) \\
  Y_{nm} &= \frac{L_{s}}{L_{n}}\Bigg(\frac{2L_{s}^2-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\bigg)^2} \pm \\
  & \frac{L^2+L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-L_{f}^2}{2L}\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{2L_{s}^2+-2L_{t}L_{s}\cos(\Theta_{nm})}{2L_{s}}\bigg)^2} \Bigg) \\
\end{align}
